Exploring and Reverse Engineering the Motives Behind API Modifications

### 2015-03-27 rmtw/a6/latex8.tex
Added cites to lehman in methodology

More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to. The data were then mapped and coded to the laws presented by (!!!). The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes. The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.

@@

A combination of the analysis between the changes to APIs, Lehman's laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1. The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.

>>>>

More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to. The data were then mapped and coded to the laws presented by \cite{lehman1980programs}. The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes. The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.

@@

A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types}\cite{lehman1980programs} allowed us to answer RQ1. The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.
